FoRTE baseline

### 2019-06-21 analysis/paper/paper.Rmd
[paper] Tweak figure sizes

```{r bigfacet-plot, fig.cap = bigfacet_cap, fig.dim = c(12, 12)}
bigfacet_cap <- paste(
  "ED2 PFT-level predictions of leaf area index (LAI) by model configuration and parameterization."
)
readd(lai_pft_plot)
```

@@

```{r within-vs-across, fig.cap = within_vs_across_cap, fig.dim = c(6, 6)}
within_vs_across_cap <- paste(
  "Comparison of parameteric uncertainty within ensembles (colored bars, colored by model type)",
  "and \"structural\" uncertainty (variance in ensemble means; black bar) by output variable.",
  "Output variables are expressed as growing season averages for all years after 1910."
)
readd(within_across_plot)
```

>>>>

```{r bigfacet-plot, fig.cap = bigfacet_cap, fig.dim = c(12, 8)}
bigfacet_cap <- paste(
  "ED2 PFT-level predictions of leaf area index (LAI) by model configuration and parameterization."
)
readd(lai_pft_plot)
```

@@

```{r within-vs-across, fig.cap = within_vs_across_cap, fig.dim = c(9, 4)}
within_vs_across_cap <- paste(
  "Comparison of parameteric uncertainty within ensembles (colored bars, colored by model type)",
  "and \"structural\" uncertainty (variance in ensemble means; black bar) by output variable.",
  "Output variables are expressed as growing season averages for all years after 1910."
)
readd(within_across_plot)
```
